The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
series of metrics...

#### Network metrics

For each multilayer network, we calculated four metrics.These included:
multidegree, graph strength, redundancy/relevance, and  layer similarity.

@@

>>>>

#### Network metrics
We used a series of metrics to characterize the multilayer networks focusing on the relevance of individual layers, 
similarity of layers and the role of individuals. We calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of unique neighbours, we measured the connective redundancy, the proportion of neighbours repeated in multiple layers, and the layer relevance, the proportion of neighbours present compared to the neighbourhood for each individual. To measure the role of individuals, we calculated the graph strength for each individual for each layer specific season and landcover context.

e focused on four aspects
of the network: “interlayer correlation and reducibility”
(i.e., correlation between layers and similarities regarding
the information contained in each one; “node versatility”
(i.e., role of each node in the connectedness and information
flow of the network); “community structure” (i.e., whether
there are subsets of nodes more tightly connected among
each other than with the rest); and “motif analysis” (i.e.,
non-random patterns of interconnection between triads).

Node based

Calculated for each layer 
and for multilayer total

For each multilayer network, we calculated a series of metrics on individual layers and  four metrics. These included:
multidegree, graph strength, redundancy/relevance, and  layer similarity.

@@

* Multidegree: sum of degree across layers. High multidegree = connected to many
individuals across layers. Low multidegree = not connected to many individuals
across layers.
